### 2018-07-23 express2018/expansion.tex
Fixed 'Definitions 2.1 and 2.2: I think is clearer if you expand the second clause and explicitly write the converse of 1.' #25

The equivalences we consider are  mainly
 \emph{weak}, in that they
abstract from the number of internal steps performed
\begin{definition}[bisimilarity]
\label{d:wb}
A process relation ${\R}$ 
 is a (weak) \emph{bisimulation} if, whenever
 $P\RR Q$, %for all $\mu$ 
we have:
\begin{enumerate}
\item 
    $P \arr\mu P'$   implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;
\item the converse of (1)
 on the actions from $Q$.
%\item if $Q  \Ar\mu   Q'$, then there is $P'$ s.t.\ $P
%\Arcap\mu  P'$ and $P' 
%\RR Q'$.
\end{enumerate}  
 $P$ and $Q$ are \emph{bisimilar},
written $P \wb
 Q$, if $P \RR Q$ for some  bisimulation $\R$.  
\end{definition}

We sometimes call bisimilarity `\emph{weak}', to
distinguish it from \emph{strong bisimilarity}, $\sim$,
obtained by replacing in the above definition   the weak answer $
Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.
Bisimilarity is not preserved by the sum operator. 
For this, Milner introduces \emph{observational congruence}, also called \emph{rooted
  bisimilarity}.
\begin{definition}[rooted bisimilarity]
\label{d:rootedBisimilarity}
Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written $P
\rapprox Q$, if we have:
\begin{enumerate}
 \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
   \Arr\mu Q'$ and $P' \wb Q'$;
\item the converse of (1) on the actions from $Q$.
\end{enumerate}
\end{definition}
% Besides reducing the rooted bisimiarity of two processes to
% the bisimilarities of their first-step transition ends, this definition also brings a proof technique for proving the
% rooted bisimiarity by constructing a bisimulation:
% \begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
% \label{l:obsCongrByWeakBisim}
% Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
% satisfies the following properties:
% \begin{enumerate}
%  \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
%    \Arr\mu Q'$ and $P' \RR Q'$;
% \item the converse of (1) on the actions from $Q$.
% \end{enumerate}
% then $P$ and $Q$ are rooted bisimilar, i.e., $P \approx^c Q$.
% \end{lemma}

>>>>

The equivalences we consider are  mainly
 \emph{weak}, in that they
abstract from the number of internal steps performed
\begin{definition}%[bisimilarity]
\label{d:wb}
A process relation ${\R}$ 
 is a \emph{bisimulation} if, whenever
 $P\RR Q$, %for all $\mu$ 
we have:
\begin{enumerate}
\item $P \arr\mu P'$ implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;\vspace{-4pt}
\item $Q \arr\mu Q'$,implies that there is $P'$ such that $P \Arcap
  \mu P'$ and $P' \RR Q'$.
% (the converse of (1) on the actions from $Q$)
\end{enumerate}  
 $P$ and $Q$ are \textbf{bisimilar},
written as $P \wb Q$, if $P \RR Q$ for any bisimulation $\R$.  
\end{definition}

We sometimes call bisimilarity the \emph{weak} one, to
distinguish it from \emph{strong bisimilarity} ($\sim$)
obtained by replacing in the above definition   the weak answer $
Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.
Bisimilarity (the weak one) is not preserved by the sum operator (except for
guarded sums). For this, Milner introduces \emph{observational congruence}, also called \emph{rooted
  bisimilarity} \cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
\begin{definition}%[rooted bisimilarity]
\label{d:rootedBisimilarity}
Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written $P
\rapprox Q$, if we have:
\begin{enumerate}
 \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
   \Arr\mu Q'$ and $P' \wb Q'$;
 \item  $Q \arr\mu Q'$ implies that there is $P'$ such that $P
   \Arr\mu P'$ and $P' \wb Q'$. %the converse of (1) on the actions from $Q$.
\end{enumerate}
\end{definition}
% Besides reducing the rooted bisimiarity of two processes to
% the bisimilarities of their first-step transition ends, this definition also brings a proof technique for proving the
% rooted bisimiarity by constructing a bisimulation:
% \begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
% \label{l:obsCongrByWeakBisim}
% Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
% satisfies the following properties:
% \begin{enumerate}
%  \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
%    \Arr\mu Q'$ and $P' \RR Q'$;
% \item the converse of (1) on the actions from $Q$.
% \end{enumerate}
% then $P$ and $Q$ are rooted bisimilar, i.e., $P \approx^c Q$.
% \end{lemma}
